### 2017-11-13 Draft2/ExternalDefinitions.tex
Make algorithms not float
Exterminate more todos

\begin{algorithm}
	\begin{algorithmic}
		\LineComment{Copies $len$ items from $source$ to $dest$}
		\State $\FuncArrayCopy(source,\ dest,\ len)$
		\State
		\LineComment{Returns a new array with length $len$}
		\State $\FuncNewArray(len)$
		\State
		\LineComment{Returns a new, empty dynamic array}
		\State $\FuncNewDynamicArray()$
	\end{algorithmic}
\end{algorithm}

@@

\begin{description}
	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of an empty dynamic array.\\
	{\HdrAssumptions} $\VarInitCapacity$ is a natural number
	\item[growth factor] Denoted by $\VarGrowthFactor$. The constant ratio of the new capacity to the old one when $\VarList$ grows.\\
	% Todo
	{\HdrAssumptions} $\VarGrowthFactor\VarInitCapacity \geq \VarInitCapacity + 1$
\end{description}

>>>>

\begin{algorithm}[H]
	\begin{algorithmic}
		\LineComment{Copies $len$ items from $source$ to $dest$}
		\State $\FuncArrayCopy(source,\ dest,\ len)$
		\State
		\LineComment{Returns a new array with length $len$}
		\State $\FuncNewArray(len)$
		\State
		\LineComment{Returns a new, empty dynamic array}
		\State $\FuncNewDynamicArray()$
	\end{algorithmic}
\end{algorithm}

@@

\begin{description}
	\item[initial capacity] Denoted by $\VarInitCapacity$; the capacity of an empty dynamic array. $\VarInitCapacity$ must be a natural number.
	\item[growth factor] Denoted by $\VarGrowthFactor$; the constant ratio of the new capacity to the old one when $\VarList$ grows. $\VarGrowthFactor$ must be greater than $1$.
\end{description}
